---
title: "assessment 1.1"
author: "Timothy To"
date: "8/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **RMarkdown editing**
**R Markdown is a file format for making dynamic documents with R. An R Markdown document is written in markdown (an easy-to-write plain text format) and contains chunks of embedded R code**

#insert data
```{r fastfood}
fastfood<-read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')
```

#**apply library**
```{r}
library(tidyverse)
library(skimr)
library(janitor)
library(dplyr)
library(reshape)
library(tidyr)
```

#**display first 10**
```{r}
head(fastfood,10)
```

#**display first 10 rows and 5 variables #7**
```{r}
knitr::kable(fastfood[1:10,1:5],"pipe")

```

#**8.Display the observations that has more than 1000 calories**
```{r}
fastfood%>%
 filter(calories>1000)
```

#**9.observations with more than 40 in total_fat and more than 80 in total_carb in a new variable called `dont_eat_this**
```{r}
dont_eat_this<-fastfood%>%
select(restaurant,item,total_fat, total_carb)%>%
filter(total_fat>40 )%>%
filter(total_carb>80)
```

```{r}
fastfood%>%
  filter(total_fat>40 )%>%
filter(total_carb>80)%>%
select(restaurant,item,total_fat, total_carb)

```
#**display observations from restaurant Mcdonalds**
```{r}
fastfood%>%
  filter(restaurant=="Mcdonalds")
```